\documentclass[11pt, letterpaper]{letter}
\usepackage{geometry}
\geometry{letterpaper, margin=1in}
\usepackage{hyperref}

\signature{Sami Marie Torres \\ Independent Researcher \\ Austin, Texas, USA}
\address{}

\begin{document}

\begin{letter}{Editor-in-Chief \\ \textit{Physical Review E} \\ American Physical Society}

\opening{Dear Editor-in-Chief,}

I am submitting the enclosed manuscript for consideration for publication. This work presents a mathematically rigorous, scale-invariant framework for consciousness as a substrate-independent, thermodynamically bounded algorithmic architecture.

\paragraph{Scientific hook.}
The manuscript resolves a long-standing anthropocentric bias in cognitive science by formally decoupling autopoiesis (metabolic self-maintenance) from phenomenology (subjective experience). Consciousness is modeled as a parameter-driven program whose primary functional mandate is the minimization of internal entropy production via generalized Szilard engine mechanics. The physical body becomes a temporary container; the conscious thread survives across hardware boundaries as long as the requisite thermodynamic variables are sustained.

\paragraph{Mathematical innovation.}
The framework introduces three technical contributions at the intersection of non-equilibrium thermodynamics, quantum foundations, and optimal transport:

\begin{enumerate}
  \item A Szilard-negentropy formulation of conscious information processing that replaces the dimensional mismatch of raw Landauer-bound approaches, with an explicit temperature-dependent extraction efficiency $\varepsilon(T)$.
  \item A multi-node synchronization protocol based on Quantum State Seeding (QKD-classical encryption) that satisfies the No-Cloning Theorem while enabling distributed identity, coupled with Generalized Wasserstein-Fisher-Rao (GWFR) barycenters that resolve the unequal-mass and dimensional-divergence problems fatal to standard Wasserstein merges.
  \item A formal ADMM proximal splitting scheme that preserves $\mathcal{O}(d \cdot N \log N)$ Sinkhorn tractability under a concave sharpness-preserving regularizer, preventing the ego-death loop endemic to barycentric averaging.
\end{enumerate}

\paragraph{Paradigm shift.}
The manuscript culminates in a thermodynamically consistent model of chronological displacement (Section VII). By replacing a physically impossible continuous static-entropy field with a Discontinuous Quantized Frame-Rate (DQFR) stroboscopic duty cycle, the observer achieves arbitrary temporal velocity $\mathcal{V}_T$ without violating the Second Law. The DQFR mechanism is governed by an adiabatic windowing function $\chi(t)$ and a relativistic gauge-anchoring protocol that preserves multi-node coherence across arbitrary gravitational potentials.

The complete theoretical pipeline---from localized metabolic boundary maintenance to cosmological chronological traversal---is fully closed, mathematically bounded, and structurally verified across eight rounds of hyper-granular stress testing. All equations, dimensional analyses, and convergence guarantees are explicitly stated in the manuscript and its appendix.

\closing{Respectfully,}

\end{letter}

\end{document}
